Simulation Tables

### 2019-07-23 mcmc_draws_2019-07-11/mcmc_draws_NOSKEW_2019-07-11/tables.Rmd
edits

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-09/mcmc_draws_NOSKEW_2019-07-09/")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

>>>>

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-11/mcmc_draws_NOSKEW_2019-07-11/")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

### 2019-07-23 mcmc_draws_2019-07-11/tables.Rmd
edits

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-09")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

load("mcmc_draws_NOSKEW_2019-07-09/class_1_est")
load("mcmc_draws_NOSKEW_2019-07-09/class_2_est")
load("mcmc_draws_NOSKEW_2019-07-09/class_3_est")

t1 <- cbind(model_component,
            params,
            true_c1,est_c1,est_c2_noskew,
            true_c2,est_c2,est_c1_noskew,
            true_c3,est_c3,est_c3_noskew)
colnames(t1) <- c("Component",
                  "Param.",
                  "True","MSN Est. (95\\% CrI)","MN Est. (95\\% CrI) ",
                  "True","MSN Est. (95\\% CrI)","MN Est. (95\\% CrI)",
                  "True","MSN Est. (95\\% CrI)","MN Est. (95\\% CrI)")
```

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1,000, J = 4, p = 2, K = 3, r = 2. 1,000 iterations were run with a burn in of 100. Missingness mechanism was MAR and P(miss) = 0. Model results for the multivariate skew normal (MSN) and multivariate normal (MN) mixtures are presented.") %>%
  kable_styling(font_size = 7) %>%
  add_header_above(c(" " = 2,"Class 1" = 3, "Class 2" = 3, "Class 3" = 3)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27) %>%
  landscape()
```

>>>>

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-11")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

load("mcmc_draws_NOSKEW_2019-07-11/class_1_est")
load("mcmc_draws_NOSKEW_2019-07-11/class_2_est")
load("mcmc_draws_NOSKEW_2019-07-11/class_3_est")

t1 <- cbind(model_component,
            params,
            true_c1,est_c1,est_c2_noskew,
            true_c2,est_c2,est_c1_noskew,
            true_c3,est_c3,est_c3_noskew)
colnames(t1) <- c("Component",
                  "Param.",
                  "True","MSN Est. (95\\% CrI)","MVN Est. (95\\% CrI) ",
                  "True","MSN Est. (95\\% CrI)","MVN Est. (95\\% CrI)",
                  "True","MSN Est. (95\\% CrI)","MVN Est. (95\\% CrI)")
```

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with $n = 1,000$, $J = 4$, $p = 2$, $K = 3$, $r = 2$. 1,000 iterations were run with a burn in of 100. Missingness mechanism was MAR and P(miss) = 0. Model results for the multivariate skew normal (MSN) and multivariate normal (MVN) mixtures are presented.") %>%
  kable_styling(font_size = 7) %>%
  add_header_above(c(" " = 2,"Class 1" = 3, "Class 2" = 3, "Class 3" = 3)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27) %>%
  landscape()
```
